%-------------------------
% Resume in Latex
% Author : Muhammad Maaz
% Based on: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.25in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Muhammad Maaz} & \\
\end{tabular*}

\vspace{-2pt}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \href{mailto:muhamamdmaaz65@gmail.com}{Email} $|$ 
  \href{https://github.com/coding-with-maaz}{GitHub} $|$ 
  \href{https://muhammad-maaz-jet.vercel.app}{Portfolio} & \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
\vspace{-4pt}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    Full-stack developer specializing in Node.js backend development and scalable web applications. Experienced in building RESTful APIs, server-side architecture, and end-to-end solutions with modern JavaScript frameworks.
  }}
\end{itemize}

%-----------EXPERIENCE-----------------
\section{Experience}
\vspace{-4pt}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-1pt]
  \small{\item{
    \textbf{Full-Stack Developer} \hfill \textit{2023 - 2025} \\
    \textit{Spark Zone Technologies} \hfill \textit{Remote} \\
    \begin{itemize}[itemsep=-1pt]
      \item Developed scalable web applications using Node.js, Express.js, and TypeScript. Built RESTful APIs and server-side architecture for production applications.
      \item Collaborated with cross-functional teams, implementing best practices for code quality, testing, and deployment.
    \end{itemize}
  }}
  
  \small{\item{
    \textbf{Full-Stack Developer} \hfill \textit{2022 - Present} \\
    \textit{Freelance} \hfill \textit{Remote} \\
    \begin{itemize}[itemsep=-1pt]
      \item Developed end-to-end web applications using React, TypeScript, and Laravel with RESTful APIs. Created cross-platform mobile apps using Flutter with real-time features.
      \item Designed scalable backend systems using Laravel and Node.js, managing MySQL/PostgreSQL databases. Delivered 15+ projects including e-commerce platforms and streaming services.
    \end{itemize}
  }}
  
  \small{\item{
    \textbf{Mobile App Developer} \hfill \textit{2021 - Present} \\
    \textit{Independent Projects} \hfill \textit{Remote} \\
    \begin{itemize}[itemsep=-1pt]
      \item Specialized in Flutter development, creating reusable packages and publishing multiple apps on Google Play Store with authentication and real-time updates.
    \end{itemize}
  }}
\end{itemize}

%-----------PROJECTS-----------------
\section{Projects}
\vspace{-4pt}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-1pt]
  \small{\item{
    \textbf{JOB2DAY - Job Board Platform} \href{https://frontend.harpaljob.com/API/JOBS}{[Link]} \href{https://github.com/coding-with-maaz/JOB2DAY-BACKEND}{[GitHub]} \\
    \textit{Tech Stack:} Node.js, Express, MySQL, Sequelize, Firebase, Flutter, TypeScript \\
    \begin{itemize}[itemsep=-1pt]
      \item Comprehensive job board platform with RESTful APIs for job postings, applications, user authentication, and notifications. Built scalable backend with Node.js and Express, supporting Flutter mobile app with real-time features.
    \end{itemize}
  }}
  
  \small{\item{
    \textbf{TAGIQ - AI Keyword Generator} \href{https://github.com/coding-with-maaz/_TAGIQ_}{[GitHub]} \\
    \textit{Tech Stack:} Node.js, Express, Puppeteer, Flutter, TypeScript \\
    \begin{itemize}[itemsep=-1pt]
      \item Intelligent keyword generator scraping trending keywords from Google, YouTube, TikTok, Bing, and Amazon using Puppeteer with Flutter mobile app support.
    \end{itemize}
  }}
  
  \small{\item{
    \textbf{ASIAN2DAY - Streaming Platform} \href{https://nazaarabox.com}{[Link]} \href{https://github.com/coding-with-maaz/NETFLEX_CLONE}{[GitHub]} \\
    \textit{Tech Stack:} Laravel, Node.js, Flutter, MySQL, React, TypeScript \\
    \begin{itemize}[itemsep=-1pt]
      \item Advanced streaming platform with live content delivery, user authentication, and real-time interactions. Built with Laravel backend, Node.js API, and Flutter mobile app.
    \end{itemize}
  }}
  
  \small{\item{
    \textbf{Medzfitt E-commerce} \href{https://medzfitt.com}{[Link]} \href{https://github.com/coding-with-maaz/Ecomerce_Store}{[GitHub]} \\
    \textit{Tech Stack:} Laravel, PHP, MySQL, Tailwind CSS, JavaScript \\
    \begin{itemize}[itemsep=-1pt]
      \item Complete Laravel-based e-commerce platform with shopping cart, product management, order processing, user reviews, and admin dashboard.
    \end{itemize}
  }}
  
  \small{\item{
    \textbf{Flutter Ads Pro} \href{https://github.com/coding-with-maaz/FLUTTER-_ADS}{[GitHub]} \\
    \textit{Tech Stack:} Flutter, Dart, Android, iOS \\
    \begin{itemize}[itemsep=-1pt]
      \item Comprehensive Flutter ads integration package supporting Android, iOS, Web, Windows, macOS, and Linux with simplified configuration.
    \end{itemize}
  }}
\end{itemize}

%--------TECHNICAL SKILLS------------
\section{Technical Skills}
\vspace{-4pt}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-1pt]
  \small{\item{
    \textbf{Frontend:} JavaScript, TypeScript, React, Next.js, HTML5, CSS3, Tailwind CSS \\
    \textbf{Backend:} Node.js, Express.js, Laravel, PHP, TypeScript \\
    \textbf{Mobile:} Flutter, Dart, Android, iOS \\
    \textbf{Database:} MySQL, PostgreSQL, SQLite, MongoDB, Firebase \\
    \textbf{DevOps \& Tools:} Git, GitHub, Docker, Firebase, AdMob, Puppeteer, REST API
  }}
\end{itemize}

%-----------EDUCATION-----------------
\section{Education}
\vspace{-4pt}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    Bachelor's Degree in Computer Science
  }}
\end{itemize}

%-------------------------------------------
\end{document}

